### 2023-10-17 paper/draft.tex
checking for alpha

\begin{align}
    \operatorname{AURC}(f) := \mathbb{E}_{x \sim p_x} \left[  \frac{\mathbb{E}_{(\tilde{x},\tilde{y})\sim p_{xy}}[\ell([f(\tilde{x})]_{1:k},\tilde{y}) \mathbb{I}[f(\tilde{x})_{k+1} > f(x)_{k+1}]]}{\mathbb{E}_{\tilde{x}\sim p_{x}}[ \mathbb{I}[f(\tilde{x})_{k+1} > f(x)_{k+1}]]} \right] \\
    \approx \frac{1}{n} \sum_{h=1}^n \frac{\frac{1}{n-1} \sum_{i\neq h} \ell([f(x_i)]_{1:k},y_i) \mathbb{I}[f(x_i)_{k+1} > f(x_h)_{k+1}]}{\frac{1}{n-1} \sum_{i\neq h} \mathbb{I}[f(x_i)_{k+1} > f(x_h)_{k+1}]}
\end{align}

@@

\begin{todolist}
\item Vectorized implementation of Definition 2
\end{todolist}

>>>>

\begin{align}
    \operatorname{AURC}(f) := \mathbb{E}_{x \sim p_x} \left[  \frac{\mathbb{E}_{(\tilde{x},\tilde{y})\sim p_{xy}}[\ell([f(\tilde{x})]_{1:k},\tilde{y}) \mathbb{I}[f(\tilde{x})_{k+1} > f(x)_{k+1}]]}{\mathbb{E}_{\tilde{x}\sim p_{x}}[ \mathbb{I}[f(\tilde{x})_{k+1} > f(x)_{k+1}]]} \right] \\
    \approx \frac{1}{n} \sum_{h=1}^n \frac{\frac{1}{n-1} \sum_{i\neq h} \ell([f(x_i)]_{1:k},y_i) \mathbb{I}[f(x_i)_{k+1} > f(x_h)_{k+1}]}{\frac{1}{n-1} \sum_{i\neq h} \mathbb{I}[f(x_i)_{k+1} > f(x_h)_{k+1}]} := \widehat{\mathrm{AURC}}(f) \\
   =\frac{1}{n} \sum_{h=1}^n \frac{ \sum_{i\neq h} \ell([f(x_i)]_{1:k},y_i) \mathbb{I}[f(x_i)_{k+1} > f(x_h)_{k+1}]}{ \sum_{i\neq h} \mathbb{I}[f(x_i)_{k+1} > f(x_h)_{k+1}]} = \frac{1}{n} \sum_{i=1}^n \alpha_i \ell([f(x_i)]_{1:k},y_i)
\end{align}

What is the formula for $\alpha_i$?  $\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{1\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{1\leq i \leq n}$?

J: Informally, $\alpha_i$ should be a value between 1 and n-1, denoting the number of instances that have higher estimated confidence than  $f(x_i)_{k+1}$.

%loss per h, multiplied by a value between 1 and N-1; linear in terms of the loss
%linear coefficients with respect to some alpha; alpha is a scalar
%calculate alphas faster than $O(N^2)$$?
%sort $(O(NlogN)$ and thresholding $O(N)$ 
%sort by k+1

@@

\begin{todolist}
\item Vectorized implementation of Definition 2
\item Write out alphas like weights (impl) in Definition 3
\end{todolist}
